Energy-optimal configurations for high-performance computing applications: automated low-impact characterization and performance optimization of shared-memory applications

### 2022-08-15 thesis/references.tex
organazing the chapters and trying to connect

>>>>

	%%%%%%%%%%% PHASES %%%%%%%%%%%

	\bibitem[Iea(2021)]{iea_2021}
	Iea, ``Data centres and data transmission networks – analysis,'' Nov 2021.
	[Online]. Available:
	\url{https://www.iea.org/reports/data-centres-and-data-transmission-networks}

	\bibitem[Cardoso(2017)]{CARDOSO201717}
	J.~M. Cardoso, J.~G.~F. Coutinho, and P.~C. Diniz, ``Chapter 2 -
	high-performance embedded computing,'' in \emph{Embedded Computing for High Performance}, J.~M. Cardoso, J.~G.~F. Coutinho, and P.~C. Diniz, Eds.\hskip
	1em plus 0.5em minus 0.4em\relax Boston: Morgan Kaufmann, 2017, pp. 17--56.
	[Online]. Available:
	\url{https://www.sciencedirect.com/science/article/pii/B9780128041895000028}

	\bibitem[Irani(2007)]{Irani2007}
	S.~Irani, S.~Shukla, and R.~Gupta, ``Algorithms for power savings,'' \emph{ACM Transactions on Algorithms}, vol.~3, p.~41, 11 2007. [Online]. Available:
	\url{https://dl.acm.org/doi/10.1145/1290672.1290678}

	\bibitem[Poellabauer(2005)]{Poellabauer2005}
	C.~Poellabauer, L.~Singleton, and K.~Schwan, ``Feedback-based dynamic voltage
	and frequency scaling for memory-bound real-time applications,'' 2005, pp.
	234--243.

	\bibitem[Saha(2012)]{Saha2012}
	S.~Saha and B.~Ravindran, ``An experimental evaluation of real-time dvfs
	scheduling algorithms.''\hskip 1em plus 0.5em minus 0.4em\relax ACM Press,
	2012, pp. 1--12. [Online]. Available:
	\url{http://dl.acm.org/citation.cfm?doid=2367589.2367604}

	\bibitem[Pietri(2014)]{Pietri2014}
	I.~Pietri and R.~Sakellariou, ``Energy-aware workflow scheduling using
	frequency scaling.''\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 9 2014, pp.
	104--113. [Online]. Available:
	\url{http://ieeexplore.ieee.org/document/7103444/}

	\bibitem[Mashayekhy(2014)]{Mashayekhy2014}
	L.~Mashayekhy, M.~M. Nejad, D.~Grosu, D.~Lu, and W.~Shi, ``Energy-aware
	scheduling of mapreduce jobs.''\hskip 1em plus 0.5em minus 0.4em\relax
	Institute of Electrical and Electronics Engineers Inc., 9 2014, pp. 32--39.

	\bibitem[Yousefi(2018)]{Yousefi2018}
	M.~H.~N. Yousefi and M.~Goudarzi, ``A task-based greedy scheduling algorithm
	for minimizing energy of mapreduce jobs,'' \emph{Journal of Grid Computing},
	vol.~16, pp. 535--551, 12 2018.

	\bibitem[Kessler(2021)]{Kessler2021}
	C.~Kessler, S.~Litzinger, and J.~Keller, ``Crown-scheduling of sets of
	parallelizable tasks for robustness and energy-elasticity on many-core
	systems with discrete dynamic voltage and frequency scaling,'' \emph{Journal
		of Systems Architecture}, vol. 115, p. 101999, 5 2021. [Online]. Available:
	\url{https://linkinghub.elsevier.com/retrieve/pii/S1383762121000175}

	\bibitem[Ajmal(2021)]{Ajmal2021}
	M.~S. Ajmal, Z.~Iqbal, F.~Z. Khan, M.~Bilal, and R.~M. Mehmood, ``Cost-based
	energy efficient scheduling technique for dynamic voltage and frequency
	scaling system in cloud computing,'' \emph{Sustainable Energy Technologies
		and Assessments}, vol.~45, p. 101210, 6 2021. [Online]. Available:
	\url{https://linkinghub.elsevier.com/retrieve/pii/S2213138821002204}

	\bibitem[Agrawal(2021)]{Agrawal2021}
	P.~Agrawal and S.~Rao, ``Energy-efficient scheduling: classification, bounds,
	and algorithms,'' \emph{Sādhanā}, vol.~46, p.~46, 12 2021. [Online].
	Available: \url{http://link.springer.com/10.1007/s12046-021-01564-w}

	\bibitem[Silva(2022)]{electronics11050689}
	V.~R.~G. da~Silva, A.~B.~N. da~Silva, C.~Valderrama, P.~Manneback, and
	S.~Xavier-de Souza, ``A minimally intrusive approach for automatic assessment
	of parallel performance scalability of shared-memory hpc applications,''
	\emph{Electronics}, vol.~11, no.~5, 2022. [Online]. Available:
	\url{https://www.mdpi.com/2079-9292/11/5/689}
